%-----------------------------------------
% Lipin Dmitriy
% Resumé
%
% URL: http://github.com/blackwithwhite666/resume
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\setromanfont{Charis SIL}
\setsansfont{Liberation Sans}
\setmonofont{Inconsolata}
\moderncvtheme[darkred]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information 
\firstname{Dmitriy}
\familyname{Lipin}
\address{ul. Chkalova 62, 71}{Orenburg, Russia}
\mobile{+7 (922) 5397446}
\email{blackwithwhite666@gmail.com}
\homepage{github.com/blackwithwhite666}

\title{Lipin Dmitriy}

\nopagenumbers{}

\begin{document}

\maketitle

\section{Education}
\cventry{2006 - 2011}{Engineer's degree, Electrical and Electronics Engineering}{Orenburg State University}{}{}{}
\section{Skills} 
  \cvline{Launguages:}{Python, PHP, JavaScript, Java}
  \cvline{Adm.:}{GNU/Linux (deb, rpm), switches, routers}
\section{Experience} 
  \cventry{2008 - 2010}{System Administrator, Engineer}{ЗАО ''Инвестэлектросвязь'' (Corbina)}{Orenburg}{}{
    \begin{itemize}
      \item Configuration and supporting network devices of broadcast access network (last-mile).
      \item Implemented monitoring system.
      \item Developed system searching hosts by MAC-addresses.
    \end{itemize}
  }
  \cventry{2009 - now}{System Administrator, Developer}{Комитет обеспечения деятельности мировых судей}{Orenburg}{}{
    \begin{itemize}
      \item Creation of network infrastructure, e-mail, proxy, IM and web servers using virtualization.
      \item Integration of backup and monitoring systems.
      \item Developed organization portal, integration of case processing system and created portal - \url{http://kodms.ru}.
    \end{itemize}
  }
  \cventry{2011 - 2012}{Developer}{Softline Company}{Orenburg}{}{
    \begin{itemize}
      \item Developing and supporting promotion web sites and \url{http://softline.ru/} sites.
      \item Implemented log collection system.
      \item Developed searching services.
    \end{itemize}
  }
  \cventry{2012 - now}{Senior developer}{ООО ''ГДЕЭТОТДОМ.РУ''}{Moscow}{}{
    \begin{itemize}
      \item Developed framework designed for creation of backend services using Thrift as RPC framework.
      \item Implemented some backend component, worked on system infrastructure (designing, creation, monitoring).
      \item Developed service that collect and aggregate statistics data.
    \end{itemize}
  }
\section{Projects}
  \cvlistitem{ThriftPool - \url{https://github.com/gdeetotdom/thriftpool}, application server for Thrift services. ThriftPool intended to serve multiple thrift services written in Python.}
\newline{}
\section{Other}
  \cvlistitem{Profile on GitHub - \url{https://github.com/blackwithwhite666}.}
  \cvlistitem{I like to solve non-trivial problem and open source. I have an experiance with *nix systems.}
  \cvlistitem{Languages - English, Russian.}
  \cvlistitem{VCS - GIT, SVN.}
\end{document}
